Combining Formal and Distributional Models of Predicate Semantics

### 2016-03-18 papers/acl2016/paper.tex

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{alg:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
\newcommand{\blank}{\underline{\hspace{.5cm}}}
\newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
\newcommand{\entity}[1]{\ensuremath{\textsc{#1}}}

\newcommand{\true}[0]{\predicate{true}}
\newcommand{\false}[0]{\predicate{false}}

@@

\title{Combining formal and distributional models of predicate semantics}

@@

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different approaches --
distributional vector space models and semantic parsing -- each with
its own advantages and disadvantages. On one hand, distributional
models produce a vector representation of the meaning of each word
from a large unlabeled text corpus. These models have broad coverage
but a shallow semantics centered around word similarity. On the other
hand, semantic parsing translates natural language into logical
queries against a formal knowledge base, such as Freebase. This
approach produces a rich compositional semantics and furthermore can
leverage structured information from the knowledge base, e.g., to
answer natural language questions. However, semantic parsers have
limited coverage as they can only represent the meanings of words that
can be mapped to knowledge base predicates. A critical question is
\emph{how do we obtain the benefits of both approaches?}

% The answer to this question has a long and rich history.  Motivated by
% , much work has been put into representing words as collections of the
% contexts in which they appear.  Recent work with neural networks and
% word embeddings have shown that these representations can be very
% useful for a number of natural language processing tasks (see, e.g.,
% the work Mikolov et al.~\shortcite{mikolov-2013-word2vec} and papers
% that cite them).  This approach to modeling semantics is appealing
% because word embeddings can be trained on unlabeled text, allowing for
% very broad coverage, although shallow, semantics.

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.28\linewidth}
    \textbf{Input Text}\\Italian architect Andrea Palladio
  \end{minipage}
%
  ~~ $\rightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\predicate{architect}(\entity{Palladio})~\land~\predicate{architect\_N/N}(\entity{Italy}, \entity{Palladio})$
  \end{minipage}

  \vspace{.2in}
  \begin{minipage}{0.5\linewidth}
    \textbf{Category models}\\
    \begin{tabular}{@{}lll}
      \predicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
      & $\omega$: & \textsc{type:architect} $\rightarrow$ .52 \\
      &           & \textsc{type:designer} $\rightarrow$ .32 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ .20 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Relation models}\\
    \begin{tabular}{@{}lll}
      \predicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ .29 \\
      &           & \textsc{/structure/architect} $\rightarrow$ .11 \\
      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ .05 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \vspace{.1in}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity models}\\
    \begin{tabular}{@{}lll}
      \predicate{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
      &           & \textsc{type:designer} $\rightarrow$ 0 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity pair models}\\
    \begin{tabular}{@{}lll}
      \predicate{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \vspace{-.1in}
  \caption{Overview of the components of our model.  Given an input text, we
  use a CCG parser and an entity linker to produce a logical form that is a
  conjunction of predicates involving the entities in the text.  For each
  predicate (both categories and relations), we learn a distributional vector
  $\theta$, as well as weights $\omega$ associated with formal features from
  Freebase (which are shortened to fit in the figure).  For each entity and
  entity pair, we also learn a distributional vector $\phi$, and we extract a
  feature vector $\psi$ from Freebase.  These models are combined to assign a
  probability to the input text, assigning a high probability to the above
  text, and a low probability to ``Italian architect Barack Obama''.}
  \label{fig:overview}
  \vspace{-.1in}
\end{figure*}

% At the same time, other researchers have found Montague's ideas about English
% as a formal language to be useful~\cite{montague-1974-english-formal-language}.
% Modern semantic parsers make use of a model-theoretic semantics that represents
% words and phrases as formal predicates.  These predicates are then typically
% mapped onto a query over a structured knowledge base, such as
% Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
% parsers to handle the compositional structure of natural language and to
% leverage large, curated knowledge sources to perform various natural language
% processing
% tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.
% However, semantic parsers are fundamentally limited by the schema of the
% ontology they are trained on---a semantic parser trained with Freebase cannot
% even represent words whose meaning has no correlate in the Freebase ontology,
% such as ``front-runner'' and ``honcho''.

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
provide a partial answer to this question with their open-vocabulary
semantic parser. This system answers compositional, fill-in-the-blank
natural language queries against Freebase, such as ``Hollywood honcho
\blank{},'' using \emph{distributional} models of predicate
semantics. The method semantically parses text to a surface logical
form containing predicates derived from the text itself, such as
$\lambda x.\predicate{honcho}(x) \land
\predicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
denotations of these predicates using distributional information from
a large, entity-linked corpus. This method combines the broad coverage
of distributional approaches with the compositionality of semantic
parsing; however, it does not use structured information from Freebase
to assist with its predictions.

In this work, we introduce new models of predicate semantics that
leverage both structured information from Freebase and distributional
information. Our key observation is that, while there is no Freebase
predicate that corresponds exactly to the meaning of ``honcho,''
Freebase \emph{does} contain predicates that \emph{partially}
represent its meaning. For example, an entity that can be called
``honcho'' is likely to have type \predicate{person}. We therefore
incorporate \emph{features} based on Freebase paths into the predicate
models of K\&M and learn per-predicate weights for these features
using distributional information (\figref{overview}). This approach
effectively learns the meaning of a word as a distributional vector
plus a \emph{weighted combination of Freebase queries}, a considerably
more expressive representation than either existing semantic parsers
or K\&M.

@@

% Thus, we extend K\&M to incorporate such features from Freebase into
% its predicate models. Our model automatically generates such features
% and learns per-predicate weights for them using distributional
% statistics.

% In this work we introduce models of predicate semantics that combine the
% benefits of both distributional and formal approaches.  While there is no
% Freebase predicate that corresponds exactly to the meaning of ``honcho'',
% Freebase \emph{does} contain many predicates that can \emph{partially}
% represent the word.  Our models extract features from Freebase that are
% correlated with words and phrases seen in natural language text, and learns
% weights for those features as additional components of a distributional model
% of the word's meaning.

% To demonstrate these models, we focus on the task of fill-in-the-blank natural
% language queries, such as ``Italian architect \blank{}''.  Similar to many
% current semantic parsers, we first convert this natural language query into a
% logical form: $\lambda x. \predicate{architect}(x) \land
% \predicate{architect\_N/N}(\entity{Italy},
% x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
% relationship between two entities mediated by the word ``architect'', as in
% ``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
% \predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
% mediated by ``architect'', but through different syntax.  N/N is how
% CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
% parser (e.g., that of Kwiatkowski et
% al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
% logical form to a single Freebase query, likely involving
% (\predicate{/people/person/nationality}: \entity{Italy}) and
% (\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
% restricting ourselves to modeling only what can be represented as a Freebase
% query, we follow Krishnamurthy and
% Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
% model for each predicate that can give a \emph{score} to potential arguments.
% The model for \predicate{architect}, e.g., should give high scores to
% \entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
% \entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
% Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
% means of finding entities in text, we inject additional information from
% Freebase into the models for each predicate.  The model we learn for
% \predicate{architect} has a \emph{feature} capturing the fact that an entity
% has the type \entity{/architecture/architect} in Freebase, and the model for
% \predicate{architect\_N/N} has a \emph{feature} capturing whether the first
% argument is the country of nationality of the second argument.  An overview of
% the components of our model is given in \figref{overview}.
% 
% This is a new kind of predicate semantics.  It is distributional---part of the
% model is still trained in a manner very similar to word2vec---yet it is also
% formal.  However, instead of committing to a single Freebase query to represent
% a phrase, as traditional formal approaches do, our models are flexible,
% encoding many possible Freebase queries as features that can give hints to the
% model.  Thus words that would be impossible to represent as a single Freebase
% query can still benefit from the information contained in Freebase---our model
% for ``front-runner'' learns that acceptable entities are politicians, even
% though there is no exact encoding of ``front-runner'' in Freebase.
% 
% The rest of this paper is organized as follows.  In \secref{background}, we
% describe the relevant background necessary to understand the models we propose,
% and we situate our model in the context of related work.  In \secref{method},
% we give a formal description of our models of predicate semantics.  In
% \secref{evaluation}, we present experimental results on fill-in-the-blank
% natural language query task.  Using web text linked to Freebase as our training
% and test data, we show a 62\% relative improvement over prior work, giving a
% new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
% detailed discussion of the benefits and drawbacks of the models we have
% proposed.  We then conclude in \secref{conclusion}.

@@

Our proposed method is best viewed as the addition of SFE
features~\cite{gardner-2015-sfe} to Krishnamurthy and
Mitchell's~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
open-vocabulary semantic parser.  Accordingly, in this section we briefly
describe both of these techniques, as well as give a short overview of other
closely related work.

@@

The truth probability of a predicate instance such as
\predicate{architect}(\entity{AndreaPalladio}) is learned using
probabilistic matrix factorization. This factorization has two sets of
parameters: each category or relation has a learned $k$-dimensional
embedding $\theta$, and each entity or entity pair has a learned
embedding $\phi$. The probability assigned to a category instance
$c(e)$ or relation instance $r(e_1, e_2)$ is given by:

@@

    \path[]
      (1) edge node [sloped, anchor=center, above] {\predicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\predicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\predicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\predicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\predicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\predicate{nationality}\textgreater\\
  \textless\predicate{designed}, \predicate{located\_in}\textgreater
  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

@@

\subsection{Other related work}

@@

For each entity and entity pair in the data we compute an SFE feature vector
$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
is a sparse binary vector containing indicator features for all edge sequences
that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
These features are shown for the entity pair (\entity{Palladio},
\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
similar features to form the sparse binary vector $\psi(e)$.  These features
are of two types: (1) edge sequences that begin at node $e$ (up to length two),
and (2) edge sequences that begin at node $e$ along with the node at the end of
the sequence.  For example, all of the features listed in \figref{sfe} for the
entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
(1) for the entity \entity{Palladio}, as well as the features
\textless\predicate{type}\textgreater and
\textless\predicate{designed}\textgreater.  Examples of of type (2) features
are \textless\predicate{type}\textgreater:\entity{architect}, and
\textless\predicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
features of type (1) capture the fact that an entity participates in particular
kinds of relations, such as designing architectural structures, while features
of type (2) capture the way an entity is related to particular other entities.
Features of type (2) are very specific, and are most useful in practice when
the entity in the feature is a type node, such as with
\textless\predicate{type}\textgreater:\entity{architect}, though occasionally
features of this type involving other entities are also selected in our feature
selection process.

@@

PMI measures the strength of association between two variables $x$ and $y$; it
is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
associate predicates with SFE features.  However, our SFE features are for each
\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
SFE features with predicates, we use the training data to find a mapping from
entities and entity pairs to predicates that they have been seen with in the
data.  For example, the phrase ``Italian architect Andrea Palladio'' is
considered a positive training example for the instantiated predicates
$\predicate{architect}(\entity{Andrea Palladio})$ and
$\predicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
then associate the feature vectors for \entity{Andrea Palladio} and
(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
\predicate{architect} and \predicate{architect\_N/N}, respectively.  For each
predicate $\pi$ and feature $f$, we use these counts to calculate the
probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
counts below some threshold, we pick the $k$ features with the highest PMI
values for each predicate to use in our model.\footnote{We used $k=100$ in this
paper.}

@@

While we largely follow the semantic parsing framework introduced by K\&M, we
made one important change in how logical forms are generated.  For the running
example we have been using this paper, ``Italian architect Andrea Palladio'',
the relation predicate produced by K\&M's system is
$\predicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  \predicate{N/N}
does correctly capture the fact that \entity{Italy} is used syntactically as a
noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
information contained in the syntax that ``architect'' was mediating that
noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
``Italian architect Andrea Palladio'' are both modeled using the same relation
predicate, which leads to a very generic and largely useless model for the
predicate \predicate{N/N}.  By splitting \predicate{N/N} into separate
predicates (\predicate{architect\_N/N} and \predicate{president\_N/N}), we give
the model the opportunity to learn more fine-grained relation semantics, and we
allow our feature selection pipeline to find much more useful features for
relation predicates.  While it would be ideal to use actual dependency
relations to determine which words to add to the predicate in complex noun
phrases, most current parsers treat these kinds of noun phrases as flat, with
all noun modifiers depending directly on the head of the noun phrase.  We
approximate this ideal by simply taking all words in between the two entities
in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
Madigan'' would produce the predicate \predicate{attorney\_general\_N/N}).

A similar issue arises with prepositions and possessives.  For a phrase such as
``Barack Obama, president of the U.S.'', K\&M's system would produce the
following relation predicate: $\predicate{of}(\entity{Barack Obama},
\entity{U.S.})$.  Because this same predicate (\predicate{of}) is used for all
instances of this preposition, the predicate is forced to model too much and
becomes overly generic.  When there is a common noun mediating a prepositional
dependency between two entities, as in the phrase above, we add that noun to
the predicate, giving the instance $\predicate{president\_of}(\entity{Barack
Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
``Rome, Italy's capital'', producing the predicate \predicate{'s\_capital}.

@@

One final way in which we improved K\&M's semantic parser is in how candidate
entities are generated during inference.  Because the distributional-only
predicate models used by K\&M's semantic parser need to learn a vector of
parameters for each entity pair, they cannot give a non-zero score to any
entity pair not seen during training time.  When given a query such as
$\lambda(\entity{x}) \predicate{architect\_N/N}(\entity{x}, \entity{Andrea
Palladio})$, K\&M's system only needs to consider the set of entities
$\entity{x}$ that have been seen at training time with \entity{Andrea
Palladio}; all other entities will get a score of 0.

@@

We evaluate our models of predicate semantics on a fill-in-the-blank natural
language query task.  Each test example is a natural language phrase containing
at least two Freebase entities, one of which is held out.  The system must
propose Freebase entities to fill in the blank left by the held out entity, and
the predicted entities are then judged manually for correctness.  We compare
our proposed models, which combine distributional and formal elements, with
distributional-only and formal-only baselines.

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, which
consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with Google's
FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training data, 3
million webpages from this corpus were processed with a CCG parser to produce
logical forms, as described in \secref{jayant-semparse}.  This produced 2.1m
predicate instances involving 142k entity pairs and 184k entities.  After
removing infrequently-seen predicates (seen fewer than 6 times), there were 25k
categories and 4.2k relations.\footnote{The differences in numbers reported
here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are due to the
improved logical form generation, discussed in \secref{better-lfs}.}

We also used the test set created by K\&M, which contains
220 queries generated in the same fashion as the training data from a separate
section of ClueWeb.  However, we used this set for intermediate evaluations
while developing our models, and so we also generated another, similar test set
from a different held out section of ClueWeb.  This final test set contains 307
queries.  We report results on both of these test sets below.  All of the data
used in these experiments is available at [url withheld for review].

>>>>

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{alg:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
\newcommand{\blank}{\underline{\hspace{.5cm}}}
\newcommand{\lexicalpredicate}[1]{\ensuremath{\textit{#1}}}
\newcommand{\formalpredicate}[1]{\ensuremath{\textsc{#1}}}
\newcommand{\entity}[1]{\ensuremath{\textsc{#1}}}

\newcommand{\true}[0]{\formalpredicate{true}}
\newcommand{\false}[0]{\formalpredicate{false}}

@@

\title{Combining Formal and Distributional Models of Predicate Semantics}

@@

How should a computer program represent the meaning of a word or a
phrase? Recent work has suggested two vastly different
approaches---distributional vector space models and semantic
parsing---each with its own advantages and disadvantages. On one hand,
distributional models produce a vector representation of the meaning
of each word from a large unlabeled text corpus. These models have
broad coverage but a shallow semantics centered around word
similarity. On the other hand, semantic parsing translates natural
language into logical queries against a formal knowledge base, such as
Freebase. This approach produces a rich compositional semantics and
furthermore can leverage structured information from the knowledge
base, e.g., to answer natural language questions. However, semantic
parsers have limited coverage as they can only represent the meanings
of words that can be mapped to knowledge base predicates. A critical
question is \emph{how do we obtain the benefits of both approaches?}

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.28\linewidth}
    \textbf{Input Text}\\Italian architect \blank{}
  \end{minipage}
%
  ~~ $\rightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\lexicalpredicate{architect}(x)~\land~\lexicalpredicate{architect\_N/N}(\entity{Italy}, x)$
  \end{minipage}

  \vspace{.2in}
  \begin{minipage}{0.5\linewidth}
    \textbf{Category models}\\
    \begin{tabular}{@{}lll}
      \lexicalpredicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
      & $\omega$: & \textsc{type:architect} $\rightarrow$ .52 \\
      &           & \textsc{type:designer} $\rightarrow$ .32 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ .20 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Relation models}\\
    \begin{tabular}{@{}lll}
      \lexicalpredicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ .29 \\
      &           & \textsc{/structure/architect} $\rightarrow$ .11 \\
      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ .05 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \begin{minipage}{0.5\linewidth}
    \textbf{Entity models}\\
    \begin{tabular}{@{}lll}
      \entity{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
      &           & $\cdots$ \\
      \entity{Obama}: & $\phi$: &[.85, .1, \ldots] \\
      & $\psi$: & \textsc{type:politician} $\rightarrow$ 1 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity pair models}\\
    \begin{tabular}{@{}lll}
      \entity{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$ \\
      \entity{(Italy, Obama)}: & $\phi$: &[-.2, -.2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 0 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \begin{minipage}{0.5\linewidth}
    \textbf{Output}\\
    \begin{tabular}{@{}ll}
      $\mathrm{prob}(\entity{Palladio})$: & 0.79 \\
      $\mathrm{prob}(\entity{Obama})$: & 0.01 \\
      $\cdots$ \\
    \end{tabular}
  \end{minipage}

  \vspace{-.1in}
  \caption{Overview of the components of our model.  Given an input
  text, we use a CCG parser and an entity linker to produce a logical
  form that is a conjunction of predicates involving the entities in
  the text.  For each predicate (both categories and relations), we
  learn a distributional vector $\theta$, as well as weights $\omega$
  associated with formal features from Freebase (which are shortened
  to fit in the figure).  For each entity and entity pair, we also
  learn a distributional vector $\phi$, and we extract a feature
  vector $\psi$ from Freebase.  These models are combined to assign a
  probability to candidate entities, assigning a high probability to
  \entity{Andrea Palladio} and a low probability to \entity{Barack
  Obama}.}
  \label{fig:overview}
  \vspace{-.1in}
\end{figure*}

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}
provide a partial answer to this question with their open-vocabulary
semantic parser. This system answers compositional, fill-in-the-blank
natural language queries against Freebase, such as ``Hollywood honcho
\blank{},'' using \emph{distributional} models of predicate
semantics. The method semantically parses text to a surface logical
form containing predicates derived from the text itself, such as
$\lambda x.\lexicalpredicate{honcho}(x) \land
\lexicalpredicate{honcho\_N/N}(\entity{Hollywood}, x)$, then learns the
denotations of these predicates using distributional information from
a large, entity-linked corpus. This method combines the broad coverage
of distributional approaches with the compositionality of semantic
parsing; however, it does not use structured information from Freebase
to assist with its predictions.

In this work, we introduce new models of predicate semantics that
leverage both structured information from Freebase and distributional
information. Our key observation is that, while there is no Freebase
predicate that corresponds exactly to the meaning of ``honcho,''
Freebase \emph{does} contain predicates that \emph{partially}
represent its meaning. For example, an entity that can be called
``honcho'' is likely to have type \formalpredicate{person}. We therefore
incorporate \emph{features} based on Freebase paths into the predicate
models of K\&M and learn per-predicate weights for these features
using distributional information (\figref{overview}). This approach
effectively learns the meaning of a word as a distributional vector
plus a \emph{weighted combination of Freebase queries}, a considerably
more expressive representation than either existing semantic parsers
or K\&M.

@@

@@

In this work, we make heavy use of the open-vocabulary semantic parser
of Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}, as
well as features derived from a knowledge base using a technique
called subgraph feature extraction~\cite[SFE]{gardner-2015-sfe}.
Accordingly, in this section we briefly describe both of these
techniques.

@@

The truth probability of a predicate instance such as
\lexicalpredicate{architect}(\entity{AndreaPalladio}) is learned using
probabilistic matrix factorization. This factorization has two sets of
parameters: each category or relation has a learned $k$-dimensional
embedding $\theta$, and each entity or entity pair has a learned
embedding $\phi$. The probability assigned to a category instance
$c(e)$ or relation instance $r(e_1, e_2)$ is given by:

@@

    \path[]
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{nationality}} (2)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (3)
      (1) edge node [sloped, anchor=center, above] {\formalpredicate{designed}} (5)
      (2) edge node [sloped, anchor=center, above] {\formalpredicate{type}} (4)
      (5) edge node [sloped, anchor=center, above] {\formalpredicate{located\_in}} (2);
  \end{tikzpicture}
  }
  \textbf{Features between \entity{Palladio} and \entity{Italy}}:\\
  \textless\formalpredicate{nationality}\textgreater\\
  \textless\formalpredicate{designed}, \formalpredicate{located\_in}\textgreater
  \caption{A subset of the Freebase graph, and some example extracted features
  between \entity{Palladio} and \entity{Italy}.  The actual Freebase relations
  and entity identifiers used are modified here to aid readability.}
  \label{fig:sfe}
\end{figure}

@@

@@

For each entity and entity pair in the data we compute an SFE feature vector
$\psi(e)$ and $\psi(e_1, e_2)$.  For entity pairs, the vector $\psi(e_1, e_2)$
is a sparse binary vector containing indicator features for all edge sequences
that connect nodes $e_1$ and $e_2$ in the Freebase graph, up to length 4.
These features are shown for the entity pair (\entity{Palladio},
\entity{Italy}) in the example graph in \figref{sfe}.  For entities, we extract
similar features to form the sparse binary vector $\psi(e)$.  These features
are of two types: (1) edge sequences that begin at node $e$ (up to length two),
and (2) edge sequences that begin at node $e$ along with the node at the end of
the sequence.  For example, all of the features listed in \figref{sfe} for the
entity pair (\entity{Palladio}, \entity{Italy}) are also valid features of type
(1) for the entity \entity{Palladio}, as well as the features
\textless\formalpredicate{type}\textgreater and
\textless\formalpredicate{designed}\textgreater.  Examples of of type (2) features
are \textless\formalpredicate{type}\textgreater:\entity{architect}, and
\textless\formalpredicate{nationality}\textgreater:\entity{Italy}.  Intuitively,
features of type (1) capture the fact that an entity participates in particular
kinds of relations, such as designing architectural structures, while features
of type (2) capture the way an entity is related to particular other entities.
Features of type (2) are very specific, and are most useful in practice when
the entity in the feature is a type node, such as with
\textless\formalpredicate{type}\textgreater:\entity{architect}, though occasionally
features of this type involving other entities are also selected in our feature
selection process.

@@

PMI measures the strength of association between two variables $x$ and $y$; it
is computed as $\log\frac{p(x,y)}{p(x)p(y)}$.  In our case, we want to
associate predicates with SFE features.  However, our SFE features are for each
\emph{entity} and \emph{entity pair}, not each \emph{predicate}.  To associate
SFE features with predicates, we use the training data to find a mapping from
entities and entity pairs to predicates that they have been seen with in the
data.  For example, the phrase ``Italian architect Andrea Palladio'' is
considered a positive training example for the instantiated predicates
$\lexicalpredicate{architect}(\entity{Andrea Palladio})$ and
$\lexicalpredicate{architect\_N/N}(\entity{Italy}, \entity{Andrea Palladio})$.  We
then associate the feature vectors for \entity{Andrea Palladio} and
(\entity{Italy}, \entity{Andrea Palladio}) with the predicates
\lexicalpredicate{architect} and \lexicalpredicate{architect\_N/N}, respectively.  For each
predicate $\pi$ and feature $f$, we use these counts to calculate the
probabilities $p(\pi, f)$, $p(\pi)$ and $p(f)$.  After removing features with
counts below some threshold, we pick the $k$ features with the highest PMI
values for each predicate to use in our model.\footnote{We used $k=100$ in this
paper.}

@@

While we largely follow the semantic parsing framework introduced by K\&M, we
made one important change in how logical forms are generated.  For the running
example we have been using this paper, ``Italian architect Andrea Palladio'',
the relation predicate produced by K\&M's system is
$\lexicalpredicate{N/N}(\entity{Italy}, \entity{Andrea Palladio})$.
\lexicalpredicate{N/N}
does correctly capture the fact that \entity{Italy} is used syntactically as a
noun modifier of \entity{Andrea Palladio}, but it leaves out the additional
information contained in the syntax that ``architect'' was mediating that
noun-noun dependency.  This means that ``U.S. president Barack Obama'' and
``Italian architect Andrea Palladio'' are both modeled using the same relation
predicate, which leads to a very generic and largely useless model for the
predicate \lexicalpredicate{N/N}.  By splitting \lexicalpredicate{N/N} into separate
predicates (\lexicalpredicate{architect\_N/N} and \lexicalpredicate{president\_N/N}), we give
the model the opportunity to learn more fine-grained relation semantics, and we
allow our feature selection pipeline to find much more useful features for
relation predicates.  While it would be ideal to use actual dependency
relations to determine which words to add to the predicate in complex noun
phrases, most current parsers treat these kinds of noun phrases as flat, with
all noun modifiers depending directly on the head of the noun phrase.  We
approximate this ideal by simply taking all words in between the two entities
in a noun phrase as the predicate (e.g., ``Illinois attorney general Lisa
Madigan'' would produce the predicate \lexicalpredicate{attorney\_general\_N/N}).

A similar issue arises with prepositions and possessives.  For a phrase such as
``Barack Obama, president of the U.S.'', K\&M's system would produce the
following relation predicate: $\lexicalpredicate{of}(\entity{Barack Obama},
\entity{U.S.})$.  Because this same predicate (\lexicalpredicate{of}) is used for all
instances of this preposition, the predicate is forced to model too much and
becomes overly generic.  When there is a common noun mediating a prepositional
dependency between two entities, as in the phrase above, we add that noun to
the predicate, giving the instance $\lexicalpredicate{president\_of}(\entity{Barack
Obama}, \entity{U.S.})$.  We do the same for possessives in phrases such as
``Rome, Italy's capital'', producing the predicate \lexicalpredicate{'s\_capital}.

@@

One final way in which we improved K\&M's semantic parser is in how candidate
entities are generated during inference.  Because the distributional-only
predicate models used by K\&M's semantic parser need to learn a vector of
parameters for each entity pair, they cannot give a non-zero score to any
entity pair not seen during training time.  When given a query such as
$\lambda(\entity{x}) \lexicalpredicate{architect\_N/N}(\entity{x}, \entity{Andrea
Palladio})$, K\&M's system only needs to consider the set of entities
$\entity{x}$ that have been seen at training time with \entity{Andrea
Palladio}; all other entities will get a score of 0.

@@

We evaluate our models of predicate semantics on a fill-in-the-blank
natural language query task.  Each test example is a natural language
phrase containing at least two Freebase entities, one of which is held
out.  The system must propose Freebase entities to fill in the blank
left by the held out entity, and the predicted entities are then
judged manually for correctness.  We compare our proposed models,
which combine distributional and formal elements, with a
distributional-only baseline from prior work.  All of the data and
code used in these experiments is available at [url withheld for
review].

@@

We use the dataset introduced by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary},
which consists of the ClueWeb09 web
corpus\footnote{http://www.lemuproject.org/clueweb09.php} along with
Google's FACC entity linking of that corpus to
Freebase~\cite{gabrilovich-2013-clueweb-entity-linking}.  For training
data, 3 million webpages from this corpus were processed with a CCG
parser to produce logical forms.  This produced 2.1m predicate
instances involving 142k entity pairs and 184k entities.  After
removing infrequently-seen predicates (seen fewer than 6 times), there
were 25k categories and 4.2k relations.  The differences in numbers
reported here versus those reported by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} are
due to our improved logical form generation, discussed in
\secref{better-lfs}.

We also used the test set created by Krishnamurthy and Mitchell, which
contains 220 queries generated in the same fashion as the training
data from a separate section of ClueWeb.  However, as they did not
release a development set in with their data, we used this set as a
development set.  For a final evaluation, we generated another,
similar test set from a different held out section of ClueWeb, in the
same fashion as done by Krishnamurthy and Mitchell.  This final test
set contains 307 queries.  We report results on both of these test
sets below.

\subsection{Models}
